Measuring the double-drift illusion with hand trajectories

### 2021-12-17 Manuscript.Rmd
restore renv in first big chunk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# First we load all custom scripts:

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# this may take a long time, but sets up the R environemt
# such that (I hope) all packages are compatible with my code:
renv::restore()

# First we load all custom scripts:
